\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=2.8cm, bottom=2.5cm, left=2.8cm, right=2.8cm, headheight=30pt]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{parskip}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{ragged2e}

% ─── Colors ───────────────────────────────────────────────────────────────────
\definecolor{milonavy}{RGB}{25, 50, 120}
\definecolor{milomid}{RGB}{60, 100, 185}
\definecolor{milogray}{RGB}{100, 105, 115}
\definecolor{milolight}{RGB}{245, 247, 252}
\definecolor{milodivider}{RGB}{210, 218, 238}

% ─── Header ───────────────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{%
  \textcolor{milonavy}{\textbf{\large MILO}}\;%
  \textcolor{milogray}{\small | Consumer Panel Data}%
}
\fancyhead[R]{\textcolor{milogray}{\small DeepmAInd B.V. \;·\; Confidential}}
\fancyfoot[R]{\textcolor{milogray}{\footnotesize \thepage}}
\renewcommand{\headrulewidth}{1.2pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{milonavy}\leaders\hrule height \headrulewidth\hfill}}
\renewcommand{\footrulewidth}{0pt}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}
\RaggedRight

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}
% ══════════════════════════════════════════════════════════════════════════════

\vspace*{0.3cm}

% ─── Recipient block ─────────────────────────────────────────────────────────
\begin{flushright}
  {\small\textcolor{milogray}{[City], [Date]}}
\end{flushright}

\vspace{4pt}

{\small
\textbf{[Contact Name]}\\
[Title]\\
[Company Name]\\
[Address]
}

\vspace{16pt}

% ─── Subject line ─────────────────────────────────────────────────────────────
\textcolor{milonavy}{\textbf{Re: Data Access Proposal - Milo Consumer Panel}}

\vspace{4pt}
\textcolor{milodivider}{\rule{\linewidth}{0.8pt}}
\vspace{10pt}

% ─── Salutation ───────────────────────────────────────────────────────────────
Dear [Contact Name],

We are writing on behalf of \textbf{Milo}, a Belgian consumer data company. This letter outlines our intent to offer \textbf{[Company Name]} access to our shopper panel, and to explore whether a commercial relationship makes sense for both parties.

% ─── Section 1 ────────────────────────────────────────────────────────────────
\vspace{8pt}
{\large\textbf{\textcolor{milonavy}{What Milo Is}}}
\vspace{2pt}

Milo collects real purchase data from Belgian consumers through a receipt-scanning app. When a consumer scans a grocery receipt, we capture exactly what was bought, where, at what price, and whether it was on promotion.

Every purchase is linked to the correct product, brand, and retailer - cross-referenced against a complete Belgian retail product database covering all major chains: Colruyt, Delhaize, Carrefour, Lidl, Aldi, and more.

\vspace{4pt}
\noindent\colorbox{milolight}{%
  \parbox{\dimexpr\linewidth-2\fboxsep\relax}{%
    \vspace{5pt}
    \textcolor{milonavy}{\textbf{The result: a live consumer panel built entirely on real purchases - not surveys, not estimates.}}
    \vspace{5pt}
  }%
}

% ─── Section 2 ────────────────────────────────────────────────────────────────
\vspace{10pt}
{\large\textbf{\textcolor{milonavy}{What We Are Offering}}}
\vspace{2pt}

We are offering \textbf{[Company Name]} subscription access to two monthly reports, delivered in standard Excel format - no software or setup required.

\vspace{6pt}
\textbf{1.\enspace SKU Performance Report}\\
{\small\textcolor{milogray}{Per product · per retailer · per month}}

\vspace{3pt}
\begin{itemize}[leftmargin=1.6em, itemsep=1pt, topsep=2pt]
  \item How many unique shoppers bought your product this month?
  \item How often do they come back?
  \item What price did they actually pay vs.\ what was on the shelf?
  \item What share of your category are you winning - and at which retailer?
  \item How effective were your promotions?
\end{itemize}

\vspace{8pt}
\textbf{2.\enspace Brand Switching Report}\\
{\small\textcolor{milogray}{Per category · per month}}

\vspace{3pt}
\begin{itemize}[leftmargin=1.6em, itemsep=1pt, topsep=2pt]
  \item Are consumers staying loyal to your brand or moving to a competitor?
  \item Which competitor are you losing buyers to - and gaining from?
  \item Are promotions bringing in new buyers or just discounting existing ones?
\end{itemize}

% ─── Section 3 ────────────────────────────────────────────────────────────────
\vspace{10pt}
{\large\textbf{\textcolor{milonavy}{Why This Matters}}}
\vspace{2pt}

Most Belgian FMCG brands today rely on expensive market research with long lead times and limited detail at the product level. Milo offers a direct, affordable alternative - real purchase data, updated monthly, with full transparency on where the numbers come from.

We are currently onboarding our first commercial clients. Companies that come on board early benefit from \textbf{preferred pricing} and a direct say in which categories and metrics we develop next.

% ─── Section 4 ────────────────────────────────────────────────────────────────
\vspace{10pt}
{\large\textbf{\textcolor{milonavy}{Proposed Next Step}}}
\vspace{2pt}

We would welcome a \textbf{30-minute call} to walk you through a sample report for your category - no commitment required at this stage.

If \textbf{[Company Name]} wishes to formally register its interest, we invite you to countersign this letter below. This is a \textbf{non-binding} expression of mutual intent to explore a commercial relationship, subject to agreeing on final terms.

We look forward to hearing from you.

% ─── Signature ────────────────────────────────────────────────────────────────
\vspace{16pt}
Kind regards,

\vspace{28pt}
\textcolor{milonavy}{\rule{6.5cm}{0.5pt}}\\[2pt]
\textbf{[Your Name]}\\
CEO, DeepmAInd B.V. - Milo\\
{\small\textcolor{milogray}{[email address] \;·\; [phone number]}}

% ─── Counter-signature ────────────────────────────────────────────────────────
\vspace{20pt}
\textcolor{milodivider}{\rule{\linewidth}{0.8pt}}
\vspace{4pt}

{\small\textbf{Expression of Interest - [Company Name]}}

{\small\textcolor{milogray}{By signing below, [Company Name] confirms its interest in learning more about the Milo consumer panel and agrees to a follow-up conversation. This signature is non-binding.}}

\vspace{22pt}

\begin{tabularx}{\linewidth}{@{}X@{\hspace{2cm}}l@{}}
  \textcolor{milonavy}{\rule{6.5cm}{0.5pt}} & \textcolor{milonavy}{\rule{3.5cm}{0.5pt}} \\[3pt]
  \textbf{[Name], [Title]} & \textbf{Date} \\
  {\small\textcolor{milogray}{[Company Name]}} & \\
\end{tabularx}

\vspace{14pt}
\textcolor{milodivider}{\rule{\linewidth}{0.8pt}}
\vspace{4pt}
{\footnotesize\textcolor{milogray}{DeepmAInd B.V. · Belgium · [email] · This document is confidential and intended solely for the named recipient.}}

\end{document}
